Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-24 Article.tex
update the eq1
update the section 4

@@

More formally, the rest of the paper derives a heuristic that aims at solving the following problem (Table \ref{table1} summarizes the main notations):
 \begin{equation}
  \min_{\substack{S \subset CS\\ |S| = N_{COAL} \\ 
     \forall s \in S,\ |s| \neq 0 \\ P_{s}^{CRCT} \geq P^{MIN}}}
  \Bigg\{ \sum_{s \in S} Pr[P_{s} \leq P_{s}^{CRCT}] \Bigg\}
  \label{problem}
\end{equation}

@@

This section explains the process with which we form the coalitions (see the third block of Figure \ref{Fig1}). First, we need to simulate the timeseries of available power (first two blocks of Figure \ref{Fig1}). We consider a pool $ \mathcal{A} $ of 200 agents, whose parameters were chosen randomly. The prosumers are positioned (also randomly) on a square lattice previously filled with climate vectors obtained from the french data sets (see section \ref{sec:model}). Simulations were run from february 2006 to december 2010 such that we are dealing with 200 hourly sampled timeseries of available power over this period. Removing season trends finally leads us to the formation of coalitions.

The model we used in order to simulate timeseries of available production provides some diversity because of the combination between the energetic mix (renewable generators combination) and the climate vectors. Nevertheless, as the number of agents grows, the timeseries tend to exhibit similar patterns. This is apparent when creating a correlation graph $ G_{1}(\mathcal{A},E_{1},\omega_{1}) $ with the same kind of metric as \cite{Garas2008} or \cite{Onnela2004} ($ d_{ij} = 1 - \rho_{ij}^{2} $), where well defined clusters appear in the $ \epsilon $-graph for any values of $ \epsilon $.

However, these clusters of strongly correlated timeseries are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show (see the green curves on figure \ref{Fig4}), as expected, terrible values (far worse than a random split of the agents in the same number of coalitions).

We thus opt for reversing the metric ($ d_{ij}^{'} = \rho_{ij}^{2} $) such that uncorrelated timeseries are close to each other and (anti)correlated timeseries are distant in $ G_{2}(\mathcal{A},E_{2},\omega_{2}) $. As expected \cite{Onnela2004}, independently of the $ \epsilon $ parameter, the resulting $ \epsilon $-graph exhibits henceforth much less clustering than in $ G_{1} $ and communities seem hardly visible. Therefore, using classical clustering or community detection algorithms seem to provide poor results.

@@

%\begin{figure}
% \centering
%  \subcaptionbox{Social Welfare\label{fig4:a}}{\includegraphics[width=1.6in]{figure7_with_green_curve_v1/uti5}}\hspace{1em}%
%  \subcaptionbox{Market entering percentage\label{fig4:b}}{\includegraphics[width=1.6in]{figure4_with_green_curve/survival2_old}}
%\caption{Evolution of the social welfare \textbf{a)} and the percentage of coalitions able to enter the market \textbf{b)} for different values of $ P_{MIN} $. Blue curves represent clique percolation, red curves, the random process, and the green ones, correlated coalitions.}
%\label{Fig4}
%\end{figure}

>>>>

\DeclareMathOperator*{\argmin}{arg\,min}

@@

More formally, the rest of the paper derives a heuristic that aims at solving the following problem (Table \ref{table1} summarizes the main notations):
 \begin{equation}
  \argmin _{\substack{ S \subset CS \\ 
                      |S| = N_{COAL} \\ 
                      \forall s \in S,\ |s| \neq 0 
                      \\ P_{s}^{CRCT} \geq P^{MIN}}}
   \sum_{s \in S}  \Pr \bigl[ P_{s} \leq P_{s}^{CRCT} \bigr]
  \label{problem}
\end{equation}

@@

This section explains the process with which we form the coalitions (see the third block of Figure \ref{Fig1}). First, we need to simulate the time-series of available power (first two blocks of Figure \ref{Fig1}). We consider a pool $ \mathcal{A} $ of 200 agents, whose parameters were chosen randomly. The prosumers are positioned (also randomly) on a square lattice previously filled with climate vectors obtained from the french data sets (see section \ref{sec:model}). Simulations were run from february 2006 to december 2010 such that we are dealing with 200 hourly sampled time-series of available power over this period. Removing season trends finally leads us to the formation of coalitions.

The model we used in order to simulate time-series of available production provides some diversity because of the combination between the energetic mix (renewable generators combination) and the climate vectors. Nevertheless, as the number of agents grows, the time-series tend to exhibit similar patterns. This is apparent when creating a correlation graph with similar metric suc as defined in \cite{Garas2008} or \cite{Onnela2004} ($ d_{ij} = 1 - \rho_{ij}^{2} $), where well defined clusters appear in the $ \epsilon $-graph for any values of $ \epsilon $.

However, these clusters of strongly correlated time-series are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show (see the green curves on figure \ref{Fig4}), as expected, terrible values (far worse than a random split of the agents in the same number of coalitions).

We thus opt for reversing the metric ($ d_{ij}^{'} = \rho_{ij}^{2} $) such that uncorrelated time-series are close to each other and (anti)correlated time-series are distant. We defined a Graph $G_\epsilon(\mathcal{A},E)$ where $\mathcal{A}$ are the agent and a edge $E$ is present if $ \rho_{ij}^{2} > \epsilon $. As expected \cite{Onnela2004}, independently of the $ \epsilon $ parameter, the resulting $ \epsilon $-graph exhibits henceforth much less clustering and communities seem hardly visible. Therefore, using classical clustering or community detection algorithms seem to provide poor results.

@@
